---
title: "BIO1007A"
author: "Andrew Planting"
date: "2023-01-31"
output: 
 prettydoc::html_pretty:
    theme: hpstr
    highlight: github
---
## Weekly Assignment 4

**Task:**

Simulate a brand new data frame (the type of data is up to you) and conduct a statistical analysis in R using 2 variables. Create a basic ggplot that goes with the analysis.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(tidyverse)
library(ggthemes)
library(ggplot2)
```

**Plan:**

I am interested in seeing if there is a differnece in avg. sepal length between species in the iris data set. X is categorical, y is continuous so the statistical test needed is a t-test/standard ANOVA
```{r}
glimpse(iris)
dIris <- select(iris, "Species","Sepal.Length")# isolating Species and sepal length from the iris data set
df_iris <- dIris %>% # creating a dataframe with species name and avg sepal length for each 
  group_by(Species) %>%
  summarize(Avg.Sepal.Length=mean(Sepal.Length))
print(df_iris)

# creating ggplot
p_iris <- ggplot(data=df_iris, aes(x=Species, y=Avg.Sepal.Length, fill=Species)) + 
  geom_bar(stat="identity", position = "dodge") +
  ylab ("Average sepal length") +
  xlab ("Species") + 
  theme_classic()
p_iris

# running ANOVA
pIris_anova <- aov(Sepal.Length~Species, data=dIris)
summary(pIris_anova)
```
